Stats

### 2022-03-18 stats/analysis.Rmd
clean up plots

```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

@@

@@

            # hedge: space between vari and reli
            nrow = 1, widths = c(1.2, 0.06, 1),
            labels = c("A", "", "")
  ),

@@

            # box: space between vari and reli
            nrow = 1, widths = c(1.2, 0.06, 1),
            labels = c("F", "", "")
  ),

>>>>

## Internal consistency
```{r intCon_hedge_data}
# take data of first reli day for internal consistency
hedge_intCon <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    testhalf = ifelse(trialNr %% 2 == 0, "even_trials", "odd_trials")
  ) %>% 
  group_by(subjID, testhalf, sample, ageInYears) %>%
  tidyboot_mean(column = abs(clickDistFromTargetCenterX)/160, na.rm = TRUE)

@@

## Test-retest reliability

@@

# Save plots

@@

            # hedge: space between vari and reli
            nrow = 1, widths = c(1, 0.06, 1),
            labels = c("A", "", "")
  ),

@@

            # box: space between vari and reli
            nrow = 1, widths = c(1, 0.06, 1),
            labels = c("F", "", "")
  ),
